link the shotgun fid and the actual sample and outcome table

### 2020-11-24 scripts/37_clean_pheno_refreshed.Rmd
was very upset about the messiness but luckily John is such a reliable guy

  dt_cart_stool_upen_samples = xlsx::read.xlsx("/Volumes/castoricenter/CAR-Tcell_and_Microbiota/U Penn/Project 11198 Sample Key.xlsx",
                                               sheetIndex = 1);
  dt_cart_stool_upen_samples = data.table(dt_cart_stool_upen_samples)
  dt_cart_stool_upen_samples = dt_cart_stool_upen_samples[!is.na(Subject.ID)]
  dt_cart_stool_upen_samples$NA. = NULL;
  dt_cart_stool_upen_samples$NA..1 = NULL;

>>>>

  dt_cart_stool_upen_samples = xlsx::read.xlsx("/Volumes/castoricenter/CAR-Tcell_and_Microbiota/U Penn/samples/archive/Project 11198 Sample Key.xlsx",
                                               sheetIndex = 1);
  dt_cart_stool_upen_samples = data.table(dt_cart_stool_upen_samples)
  dt_cart_stool_upen_samples = dt_cart_stool_upen_samples[!is.na(Subject.ID)]
  dt_cart_stool_upen_samples$NA. = NULL;
  dt_cart_stool_upen_samples$NA..1 = NULL;

### 2020-11-24 scripts/38_link_shotgun_fid_with_pheno.Rmd
was very upset about the messiness but luckily John is such a reliable guy

@@

@@

There are sevreral NA in the CR and tox in the baseline samples

Can you please clarify what “-B” when it is noted on the patient ID (pid)?
The “-B” for Patient ID CMT001B (sample ID “CMT001 PRE-BMT”) refers to a subsequent infusion for patient CMT001. Patient ID CMT001 after 42 days from his CAR T infusion received a BMT and it was recorded as Patient ID CMT001B and sampleID CMT001 PRE-BMT . Do not include Patient ID CMT001B and sampleID CMT001 PRE-BMT in the analysis

Can you please note once more the patients that should be excluded?
Exclude the patients in sponsored trial: CMT009; CMT011N; CMT013-B
Exclude the patients CMT001B for the reason at point “1”

so I think, CMT009; and ; CMT013-B ignore
what about CMT012 and CMT004B

>>>>

## current shotgun lookup table

```{r}
source('~/db_connect_simple.R')
connect_database(config_file = '~/dbConfig.txt')
get_table_from_database('shotgun_lookup_ad')

list_table_from_database('bile')
```

@@

## Italy data

@@

```{r}
# fix some more problems in the table including the duplicated sampleids

# now John has cleaned table and added a tab about ineligible patients 
ineligible <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Italy/Pt info/italy_essential_data_v4.xlsx', sheet = 2)

italy <- read_csv('../data/shotgun_pheno/italy_pheno_earlier.csv') %>% 
  # remove the row with many NA since it is a duplicate of CMT006-dm3
  filter(!is.na(sampleid)) %>% 
  # remove the ones that are ineligible
  filter(!pid %in% ineligible$pt_id) %>% 
  select(directory:fid, pid:sampleid, oligoid)

# now load the outcome for each eligible patient
eligible <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Italy/Pt info/italy_essential_data_v4.xlsx', sheet = 1) %>% 
  rename(pid = pt_id)

italy_all <- italy %>% 
  left_join(eligible) %>% 
  filter(!is.na(disease)) # remove the ones that have NA since they are not in the eligible patients tab either

# the sub table to be updated to shotgun lookup table
italy_up <- italy_all %>% 
  select(directory, projectID, sampleid, fid)

```{r}

df %>% 
  write_csv('/Volumes/vandenbrinklab/Angel_Dai/Full_human_shotgun_catalog/shotgun_italy_earlier.csv')
```

## Upenn data

```{r}

## Update the new shotgun samples to the database table

```{r}
source('../../../microbiome_db/SQL/scripts/upload_data_from_query_OTU_AD.R')
upload_data_from_query_OTU(1) # changed the file path of the table getting uploaded 
```
